Classless Java

### 2015-10-09 paper/sections/Formalization.tex
Formalization for interface typing complete. Now is all in a single rule

\[
\inferrule{
\forall i\in 1\ldots n\ \Gamma,\Gamma^{\mh_i}\vdash\e_i\in \_\subtype\C^{\mh_i}\\
\forall\mh\in \mhs \mbox{ such that }
\mBody(\m^\mh,\C)=\method;\mh\subtype\mh^\method\\
\forall\m \mbox{ such that }
\mBody(\m,\C)\in\{\mh\QM;,\conflicted\mh\QM;\} \exists \mh_i \in\mhs\mbox{ such that }\mh_i\subtype\mh\\
\Gamma=\Gamma',\f_1{:}\T_1,\ldots,\f_k{:}\T_k,\,\QM{this}{:}\C\\
\mhs=\mh_1\ldots\mh_n
}{
\Gamma' \vdash\QM{new}\ \C\oR\cR\oC\T_1\ \f_1\QM;\ldots\T_k\ \f_k\QM;\
\mh_1\oC\QM{return}\ \e_1\QM{;}\!\cC
\ldots
\mh_n\oC\QM{return}\ \e_n\QM{;}\!\cC
\cC
\in\C
}
\quad \textsc{(T-Obj)}
\]

\subsubsection{Method Typing}

\begin{comment}
\[
\inferrule
{ }
{T_0 \spc m(\overline{T} \spc \overline{x}); \text{ OK IN I} }
\quad \textsc{(T-Meth)}
\]

\[
\inferrule
{\overline{x}:\overline{T} \vdash e:S \\ S <: T_0}
{T_0 \spc m(\overline{T} \spc \overline{x}) \text{ \{ return } e;\} \text{ OK IN
    I} \\\\ \Gamma \vdash \textbf{this}:I }
\quad \textsc{(T-MethBody)}
\]
\end{comment}

@@

\subsubsection{Interface Typing}
\[ \inferrule
{\textbf{interface } I \textbf{ extends } \overline{J} \{ \overline{M} \} \\\\
 \forall J_i \in \overline{J}, J_i \text{ OK} \\\\
 \forall m \in \overline{M}, \textsf{mbody}(m,I) \neq \error \\\\
 \forall J_i \in \overline{J}, \forall m \text{ inside } J_i,
 \textsf{mbody}(m,I) \neq \error }
{I \text{ OK}}
\quad \textsc{(T-Intf)}
 \]

Interface $I$ type checks well, if:
\begin{itemize}
\item All its super-interfaces $\overline{J}$ OK.
\item All methods inside interface $I$ are OK.
\item All methods that $I$ is inheriting from super-interfaces are OK.
\end{itemize}

\subsubsection{Context}
\[ \Gamma :: = \overline{x}:\overline{C} \]

The environment $\Gamma$ is a mapping from variables to types, written
$\overline{x}:\overline{C}$. Typing statement $\Gamma \vdash t:C$ reads ``in the
environment $\Gamma$, term $t$ has type $C$.'' We abbreviate typing statements on
sequences in a simple way, writing $\Gamma \vdash \overline{t}:\overline{C}$ as
shorthand for $\Gamma \vdash t_1:C_1,..., \Gamma \vdash t_n:C_n$.

\subsubsection{Subtyping}

@@

\subsubsection{Functional notation}
We allows functional notation for set of methods $\methods$, using the method name $\m$ as a key.
That is, we define $\methods(\m)=\method$ iff there is a unique $\method\in\methods$ whose name is $\m$.
For convenience, we define $\methods(\m)=\none$ otherwise.

\subsubsection{Auxiliary function:\mBody}

>>>>

\[
\inferrule[(T-Obj)]{
\forall i\in 1\ldots n\ \Gamma,\Gamma^{\mh_i}\vdash\e_i\in \_\subtype\C^{\mh_i}\\
\forall\mh\in \mhs \mbox{ such that }
\mBody(\m^\mh,\C)=\method;\mh\subtype\mh^\method\\
\forall\m \mbox{ such that }
\mBody(\m,\C)\in\{\mh\QM;,\conflicted\mh\QM;\} \exists \mh_i \in\mhs\mbox{ such that }\mh_i\subtype\mh\\
\Gamma=\Gamma',\f_1{:}\T_1,\ldots,\f_k{:}\T_k,\,\QM{this}{:}\C\\
\mhs=\mh_1\ldots\mh_n
}{
\Gamma' \vdash\QM{new}\ \C\oR\cR\oC\T_1\ \f_1\QM;\ldots\T_k\ \f_k\QM;\
\mh_1\oC\QM{return}\ \e_1\QM{;}\!\cC
\ldots
\mh_n\oC\QM{return}\ \e_n\QM{;}\!\cC
\cC
\in\C
}
\]

\subsubsection{Interface and method Typing}

\[ \inferrule[(T-Intf)]{
IT(\C_0) = \ann\ \QM{interface}\ \C_0\ \QM{extends}\ \C_1\ldots\C_n \oC\methods\cC\\\\
 \forall \QM{default}\ \mh\oC\QM{return}\ \e\QM;\cC \in \methods,
\ \Gamma^{\mh},\,\QM{this}{:}\C\vdash\e\in \_\subtype\C^{\mh} \\\\
\dom(\C_0)=\dom(\C_1)\cup\ldots\cup\dom(C_n)\cup\dom(\methods)
 }{
I \text{ OK}
}
 \]

We use $\dom(\C)$ to denote the set of methods that are defined for type $\C$, that is: $\m\in\dom(\C)\ \miff \ \mBody(\m,\C)=\method$.

\begin{comment}
\subsubsection{Method Typing}

\[
\inferrule
{ }
{T_0 \spc m(\overline{T} \spc \overline{x}); \text{ OK IN I} }
\quad \textsc{(T-Meth)}
\]

\[
\inferrule
{\overline{x}:\overline{T} \vdash e:S \\ S <: T_0}
{T_0 \spc m(\overline{T} \spc \overline{x}) \text{ \{ return } e;\} \text{ OK IN
    I} \\\\ \Gamma \vdash \textbf{this}:I }
\quad \textsc{(T-MethBody)}
\]

@@

\[ \inferrule
{\textbf{interface } I \textbf{ extends } \overline{J} \{ \overline{M} \} \\\\
 \forall J_i \in \overline{J}, J_i \text{ OK} \\\\
 \forall m \in \overline{M}, \textsf{mbody}(m,I) \neq \error \\\\
 \forall J_i \in \overline{J}, \forall m \text{ inside } J_i,
 \textsf{mbody}(m,I) \neq \error }
{I \text{ OK}}
\quad \textsc{(T-Intf)}
 \]

Interface $I$ type checks well, if:
\begin{itemize}
\item All its super-interfaces $\overline{J}$ OK.
\item All methods inside interface $I$ are OK.
\item All methods that $I$ is inheriting from super-interfaces are OK.
\end{itemize}
\end{comment}
\subsubsection{Context}
\[ \Gamma :: = \overline{x}:\overline{C} \]

The environment $\Gamma$ is a mapping from variables to types, written
$\overline{x}:\overline{C}$. Typing statement $\Gamma \vdash t:C$ reads ``in the
environment $\Gamma$, term $t$ has type $C$.'' We abbreviate typing statements on
sequences in a simple way, writing $\Gamma \vdash \overline{t}:\overline{C}$ as
shorthand for $\Gamma \vdash t_1:C_1,..., \Gamma \vdash t_n:C_n$.
\marco{Something is wrong, do you really want to repeat $\Gamma$? do we ever really need the bars here?}
\subsubsection{Subtyping}

@@

\subsubsection{Functional notation}
We allows functional notation for set of methods $\methods$, using the method name $\m$ as a key.
That is, we define $\methods(\m)=\method$ iff there is a unique $\method\in\methods$ whose name is $\m$.
For convenience, we define $\methods(\m)=\none$ otherwise;
moreover $\m\in\dom(\methods)\ \miff\ \methods(\m)=\method$.
\subsubsection{Auxiliary function:\mBody}
